\documentclass{beamer}
\usetheme{Berlin}
\title{Challenges in cloud computing tokens}
\author{Joseph Wang}
\date{\today}
\begin{document}
\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Blockchain and cloud computing}
  Bitcoin has produced the world's most powerful supercomputer.  So
  how do we get this technology to general computing?
\end{frame}

\begin{frame}
  \frametitle{Introducing the power grid}
  The power grid is very powerful because you just plug in something
  and it works.  You plug in an ice cream maker.  It gets power from a
  solar, hydro, or nuclear power plant.  You don't care where the
  power comes from, and the plant doesn't care what you use the power
  for.
\end{frame}

\begin{frame}
  \frametitle{Compute power *could* work this way, but it doesn't}
  You should be able to plug in a terminal into an outlet, pay your
  fee, and get unlimited computer power.  But you can't.  Right now
  it's as if every time you need electric power they send a battery
\end{frame}

\begin{frame}
  \frametitle{Plug and play cloud computing}
  Three layers
  \begin{itemize}
  \item Application layer
  \item Communications layer - Money goes in CPU power go out
  \item Computation layer
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Problem is at the interfaces}
  Three layers
  \begin{itemize}
  \item Application to communications interface - Writing code is very
    expensive.  How do you redo existing code to run on the cloud
  \item Communcations to computation interface - How do you do metering?
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Application/communications interface}
  How do you containerize the job to be run?  Most code will consist
  of existing code and how to you retrofit code to the cloud
  interface?

  Chicken/egg and vendor lock-in issues.  How do you get enough
  interest in the grid so that people will program the initial
  application.  How do you prevent the interface from being a point of
  control.
\end{frame}

\begin{frame}
  \frametitle{Communications/computation interface}
  How do you meter the computing engine?  Problem is that there is no
  standardized unit of compute power.  How do you interface the system
  with new technology?

  Yes, I can maybe meter a CPU, but what happens if I want to connect
  a GPU or a CPU with better cache.  Or what if I want to connect a
  ASIC hardware system or quantum computer?
\end{frame}

\begin{frame}
  \frametitle{Existing solutions to the interface problem}
  \begin{itemize}
  \item Amazon
  \item BOINC and non-profit science computing
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Amazon}

 Jeff Bezos started in the 1990's with the idea of scavanging compute
 power from home computers.  Ended up with Amazon Web Services.  Use
 virtualization to containerize existing applications.  Buy your own
 backend systems.  Successful use of ``embrace, extend, extinguish''

 Problem: This architecture is a closed system that leads to vendor
 lock-in.  Intentionally no way of adding to the ecosystem.  Wonderful
 if you are Amazon.  Terrible if you are computing with Amazon
\end{frame}

\begin{frame}
  \frametitle{BOINC}

  Solve the metering problem by having solving non-profit problems.
  Creates a pool of computing machines that allow for a custom
  applications.  The fact that applications have to be specially
  written to be ``non-profit'' is a feature.

  Problem: Yes.  I'm willing to donate my computer to find space
  aliens or cure cancer.  Not willing to donate computing time to a
  bank or big-pharam company.  Also the fact that the compute purpose
  has to be non-profit means that there is no abstraction between the
  problem and the computer.
\end{frame}

\begin{frame}
  \frametitle{World Wide LHC Computing Grid}
  Get a lot of universities to pull compute resources.  Pool of
  resources allows users to write custom applications.

  Problem: Scaling problems.  What happens if you aren't a particle
  physicist?  The WWLCG is reaching capacity limits.
\end{frame}

\begin{frame}
  \frametitle{New solutions}
  \begin{itemize}
    \item Work on scalable infrastructure
    \item Federate backend systems
    \item Focus on storage and not compute
    \item Charge for solutions and not compute time <-----
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Work on framework}
  \begin{itemize}
    \item This infrastrcture can work for private clouds and public
      clouds
    \item Have tech make it possible to ``plugin'' interfaces
    \item Can create an ad-hoc compute network.  Or use the global
      compute network
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Federate compute power}
  \begin{itemize}
    \item Everyone that isn't Amazon is fighting Amazon
    \item Buy compute power from regional compute centers
    \item Resell compute power.  Separate marketing from backend
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Focus on compute storage and not power}
  \begin{itemize}
  \item Compute storage can be metered - look at storage
  \item Filecoin and storj are trying but they don't have the marketing
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{BUT LET'S GO CRAZY!!!!}
  \begin{itemize}
  \item Aliens give you a super quantum computer
  \item How do you connect it to the grid?
  \item Look at the bitcoin blockchain - You don't care how they do it
  \item So people create custom compute solutions!!!
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{BUT LET'S GO CRAZY!!!!}
  \begin{itemize}
  \item Aliens give you a super quantum computer
  \item How do you connect it to the grid?
  \item Look at the bitcoin blockchain - You don't care how they do it
  \item So people create custom compute solutions!!!
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Worlds biggest supercomputer}
  \begin{itemize}
  \item Offer up a bounty for a riddle
  \item Coin is in escrow
  \item First person with a verified solution gets the coin
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Riddles and bountys}
  \begin{itemize}
  \item Create riddles for standard problems
  \item Interface standard problems with standard libraries (BLAS and Numpy)
  \item Bootstrap with private network
  \item Once coins are available people can get bounty
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{What needs to be done?}
  \begin{itemize}
  \item Bootstrap with a prototype (small customer)
  \item Create scientific library
  \item Guerrilla marketing to corporates
  \end{itemize}
\end{frame}
\end{document}.  
