\documentclass{beamer}
\title {Rethinking Blockchain}
\author{Joseph Chen-Yu~Wang}
\institute{Bitquant Research Laboratories (Asia) Limited}
\date{\today}
\usetheme{Dresden}
\usecolortheme{beaver}
\begin{document}
\frame{\titlepage}
\begin{frame}
  \frametitle{Inconvenient questions}
  \begin{itemize}
  \item With all of the hype, where are the killer apps?
  \item Are we doing something basically wrong?
    \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Inconvenient truths}
  \begin{itemize}
  \item Blockchain *will not work* for business process improvement
  \item Magic bullet solutions for deep problems (IT and Regulatory)
  \item Legacy systems are pretty darn good
  \item Massive costs for systems integration
  \item Internal sabotage - To have this work you need the
    cooperation of people that will be fired if this works
  \item Blockchain will only generate savings if you work across
    industries
  \item Too much money.  If you have a ton of money, why do you have
    to be efficient?
  \end{itemize}
\end{frame}
\begin{frame}
  \frametime{The internet / China strategy won't work}
  \begin{itemize}
    \item You could make huge money by taking any existing
      business and just adding ``with the internet'' or ``in China''
    \item I train bears to ride bicycles.
    \item I can make a new business by training bears to ride bicycles
      with the internet.  Or by training bears to ride bicycles in
      China
    \item This won't work with blockchain
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Solutions}
  \begin{itemize}
  \item Don't use blockchain to revamp old systems
  \item Need to use blockchain for totally new products
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{What we are doing}
  \begin{itemize}
  \item Using new tech to create market for SME convertible notes
  \item Using blockchain to create new supply chain for coffee
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Get it to work small then scale up}
  \begin{itemize}
  \item The size of the transactions are USD 1000.
  \item Can't make money with that?  We are using new tech so that
    you can make money with these sized transactions
  \item Regulation?  I just have to worry about one regulator.
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Don't get sucked in by the system}
  \begin{itemize}
  \item The system is broken
    \item By sucking startups into the system, you are breaking the
      startups.
  \end{itemize}
\end{frame}
\end{document}

